Fluid-mechanical erosion creates anisotropic porous media

### 2022-05-29 docs/PhysicsPaper/StokesErosion.tex
working on sec 3

%-----------------------------------------------------------------------------------------------%
\section{Boundary Integral Equation and Cauchy Integral Formulation}
\label{sec:DLP}
%-----------------------------------------------------------------------------------------------%
To accurately and efficently solve the Stokes
  equations~\eqref{eqn:StokesEq}, we reformulate the system as a
  boundary integral equation (BIE). We represent the velocity as the sum
  of a double-layer potential and a combination of Stokeslets and
  rotlets~\cite{pow-mir1987}
\begin{align}
  \uu(\xx) = \DDD[\eeta](\xx) = \frac{1}{\pi}\int_{\bd\Omega} 
    \frac{\rr \cdot \nn}{\rho^2} \frac{\rr \otimes \rr}{\rho^2}
    \eeta(\yy) \, ds_\yy, + \sum_{\ell=1}^{M}\left(S[\llambda_\ell](\xx) +
    R[\xi_\ell](\xx)\right), \quad \xx \in \Omega.
  \label{eqn:velocityDLP}
\end{align}
Note that $\bd\Omega$ includes both the eroding bodies and the outer
  boundary. The Stokeslet and the rotlets are
  \begin{align}
    S[\lambda_\ell](\xx) = \frac{1}{4\pi} \left(\log \rho_\ell +
    \frac{\rr_\ell \otimes \rr_\ell}{\rho_\ell^2} \right) \llambda_\ell,
    \quad
    R[\xi_\ell](\xx) = \frac{\rr_\ell^\perp}{\rho_\ell^2}\xi_\ell,
  \end{align}
  where $\rr_\ell = \xx - \cc_\ell$, $\rho_\ell = \|\rr_\ell\|$, and
  $\cc_\ell$ is a point inside body $\ell$.

>>>>

%-----------------------------------------------------------------------------------------------%
\section{Boundary Integral Equation and Cauchy Integral Formulation}
\label{sec:DLP}
%-----------------------------------------------------------------------------------------------%
To accurately and efficently solve the Stokes
  equations~\eqref{eqn:StokesEq}, we reformulate the system as a
  boundary integral equation (BIE). We represent the velocity as the sum
  of a double-layer potential and a combination of Stokeslets and
  rotlets~\cite{pow-mir1987}
\begin{align}
  \uu(\xx) = \DDD[\eeta](\xx) + \sum_{\ell=1}^{M}\left(
    S[\llambda_\ell](\xx) + R[\xi_\ell](\xx)\right), 
    \quad \xx \in \Omega,
  \label{eqn:velocity}
\end{align}
where 
\begin{align}
  \DDD[\eeta](\xx) = \frac{1}{\pi}\int_{\bd\Omega} 
  \frac{\rr \cdot \nn}{\rho^2} \frac{\rr \otimes \rr}{\rho^2}
  \eeta(\yy) \, ds_\yy.
  \label{eqn:velocityDLP}
\end{align}
Note that $\bd\Omega$ includes both the eroding bodies and the outer
boundary. The Stokeslet and the rotlets are
\begin{align}
  S[\lambda_\ell](\xx) = \frac{1}{4\pi} \left(\log \rho_\ell +
  \frac{\rr_\ell \otimes \rr_\ell}{\rho_\ell^2} \right) \llambda_\ell,
  \quad
  R[\xi_\ell](\xx) = \frac{\rr_\ell^\perp}{\rho_\ell^2}\xi_\ell,
\end{align}
where $\rr_\ell = \xx - \cc_\ell$, $\rho_\ell = \|\rr_\ell\|$, and
$\cc_\ell$ is a point inside body $\ell$.

It is convenient to write equation~\eqref{eqn:velocityDLP} in terms of
complex variables. With this reformulation, analytic function theory can
be used to show that a particular quadrature rule achieves spectral
accuracy. We identify $\xx = (x_1,x_2)$ with $x = x_1 + ix_x$, and use
similar notation for $\yy$, and $\nn$. Then, the Stokes double-layer
potential is 
\begin{align}
  \DDD[\eta](x) = \pderiv{}{x} \Re \frac{1}{2\pi i} \int_\Gamma
    \frac{\overline{y \eta(y)}}{x-y} dy + 
\end{align}
